\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}
\usepackage{microtype}
\usepackage{xcolor}
\DisableLigatures{encoding = *, family = *}
\microtypesetup{expansion=false}

% Personal information
\name{ Vincent Palmer }{ }
\address{ Berlin, GermanyBerlin }
\phone{ +49 173 2445094 }
\email{ shift@someone.section.me }

\begin{document}
\makecvtitle


\section{Summary}
Senior SRE & Platform Engineering leader with 30+ years experience scaling infrastructure from startups to Fortune 500 environments. Specialize in Kubernetes, distributed systems, and enterprise platform engineering with track record of successful architecture implementation.



\section{Work Experience}

\cventry{}{Independent Consultant & Architect}{Independent Consultant & Architect}{ Berlin, Germany }{ Present }{ Advised early-stage AI/Fintech startup on technical architecture, cloud infrastructure, and security practices under strict NDA. }

  
  \item{ Provided strategic technical consulting to early-stage AI/Fintech startup, advising on foundational architecture, cloud infrastructure, and security practices under strict NDA. }
  
  \item{ Researched and developed multiple advanced systems as personal projects, including a multi-RAFT distributed key-value store, an ML-powered HTTP/3 WAF, and an AI-native development platform. }
  


\cventry{}{Chief Architect}{MedTech Startup}{ Berlin }{ Present }{ Architected and led end-to-end implementation of greenfield prescription delivery platform, serving 10,000+ daily users with 99.95% uptime. }

  
  \item{ Led cross-functional team of 8 engineers through complete platform lifecycle from concept to production deployment. }
  
  \item{ Directed architectural strategy for HIPAA-compliant prescription management, achieving regulatory approval in 6 months. }
  
  \item{ Spearheaded French market expansion, implementing local compliance requirements and achieving 20% market penetration in first year. }
  


\cventry{}{Principal Kubernetes Engineer}{Feedzai SA}{ Coimbra }{ Present }{ Served as company Kubernetes Subject Matter Expert (SME), architecting migration of core FinTech platform to K8s. }

  
  \item{ Served as company Kubernetes Subject Matter Expert (SME), architecting migration of core FinTech platform to K8s, achieving 99.9% availability and reducing infrastructure costs by 35%. }
  
  \item{ Pioneered Crossplane implementation for unified Infrastructure as Code platform, enabling seamless multi-cloud deployments across AWS, GCP, and on-premise with 40% reduction in provisioning time. }
  
  \item{ Transformed CI/CD and security paradigms, implementing software supply chain security (Attestations/SBOMs) and next-generation internal developer platform, reducing deployment time by 60%. }
  
  \item{ Established SRE practices including SLI/SLO design, error budget management, and automated incident response, reducing MTTR from 2 hours to 15 minutes. }
  


\cventry{}{Head of Systems & Infrastructure}{Booming Games Ltd}{ Berlin }{ Present }{ Built and led high-performing SRE, Test Automation, and Systems Administration teams (15+ engineers) ensuring 99.95% platform reliability for global B2B gaming platform serving 10M+ daily active users. }

  
  \item{ Built and led high-performing SRE, Test Automation, and Systems Administration teams (15+ engineers) ensuring 99.95% platform reliability for global B2B gaming platform serving 10M+ daily active users. }
  
  \item{ Engineered hybrid infrastructure spanning 5+ bare-metal datacenters and public clouds (AWS, GKE), implementing bare-metal Kubernetes clusters achieving 50% cost savings compared to managed cloud services. }
  
  \item{ Established comprehensive observability framework with Prometheus, Grafana, and ELK Stack, providing real-time insights into system performance and reducing incident detection time by 80%. }
  
  \item{ Implemented chaos engineering practices and automated failure recovery systems, improving system resilience and reducing unplanned downtime by 90%. }
  


\cventry{}{Cloud Architect}{KIWI.KI GmbH}{ Berlin }{ Present }{ Led complete migration of IoT infrastructure from legacy VMs to modern Kubernetes-based architecture. }

  
  \item{ Led complete migration of IoT infrastructure from legacy VMs to modern Kubernetes-based architecture, achieving zero-downtime migration for apartment door access control system serving 10,000+ units. }
  
  \item{ Implemented comprehensive CI/CD pipeline from scratch using Jenkins and GitLab CI, reducing deployment time by 75% and eliminating manual deployment errors. }
  
  \item{ Executed critical Python 2 to Python 3 migration across entire codebase (50+ services), ensuring continued security support and improved performance by 30%. }
  


\cventry{}{Senior DevOps Engineer}{ChartMogul Ltd}{  }{ Present }{ Championed DevOps methodologies and automation across engineering department. }

  
  \item{ Championed DevOps methodologies and automation across engineering department, fostering an agile culture that significantly accelerated development and deployment cycles. }
  
  \item{ Managed a diverse environment including early-adoption Kubernetes, Docker, and traditional VMs. }
  


\cventry{}{Systems Administrator}{Performance Horizon Group}{ Newcastle upon Tyne, UK }{ Present }{ Established formal change and release management process. }

  
  \item{ Established a formal change and release management process from ground up, implementing automated deployments to improve reliability and velocity. }
  
  \item{ Architected and deployed a highly available IDS/IPS/NSM solution to enhance platform security. }
  


\cventry{}{DevOps Engineer & R&D}{Odobo Limited}{ Gibraltar }{ Present }{ Architected and implemented a continuous delivery platform. }

  
  \item{ Architected and implemented a continuous delivery platform integrating JIRA and Bitbucket, automating the full software delivery lifecycle. }
  
  \item{ Led successful consolidation of multiple configuration management tools into a single, unified Salt-based platform, improving consistency and reducing complexity. }
  


\cventry{}{System Engineer}{William Hill Online}{ Gibraltar }{ Present }{ Managed all production and pre-production deployments in a high-stakes, PCI-DSS compliant online gaming environment. }

  
  \item{ Managed all production and pre-production deployments in a high-stakes, PCI-DSS compliant online gaming environment. }
  
  \item{ Engineered novel deployment techniques that reduced application downtime and streamlined release process. }
  


\cventry{}{Freelance Consultant}{ticki.sh}{ Newcastle upon Tyne, UK }{ Present }{ Freelance consulting services. }


\cventry{}{Lead Architect}{The Amazing Group}{ Gateshead, UK }{ Present }{ Lead architectural responsibilities. }





\section{Education}

\cventry{}{}{Linux Community}{  }{ Present }{ Linux user since 1994, Advanced Systems Programming expertise throughout career }

\cventry{}{}{Professional Development}{  }{ Present }{ 30+ years continuous professional development in emerging technologies }




\section{Skills}

\textbf{ Site Reliability Engineering: } SLO/SLI Design, Error Budget Management, Chaos Engineering, MTTR Reduction, Incident Response, Blameless Post-Mortems, Toil Automation

\textbf{ Cloud & Containerization: } JavaScript, TypeScript, Node.js, React, Vue.js

\textbf{ Infrastructure as Code: } Crossplane, Terraform, Salt, Ansible, Puppet, Helm

\textbf{ CI/CD & GitOps: } GitHub Actions, Jenkins, GitLab CI, ArgoCD, Flux, Pipeline Automation

\textbf{ Observability & Monitoring: } Jenkins, GitLab CI, Terraform, Docker, Kubernetes

\textbf{ Programming Languages: } Go, Python, Rust, Bash, C/C++, Perl, Ruby, Erlang, PHP, Java

\textbf{ Security & Compliance: } Software Supply Chain (SBOMs, Attestations), HashiCorp Vault, IDS/IPS, PCI-DSS, Zero Trust

\textbf{ Platform Engineering: } Internal Developer Platforms (IDP), Developer Experience (DevEx), Service Mesh, Istio



\end{document}